\ZpL: a p-adic precision package

### 2018-01-31 ZpL/ZpL.tex
Section 2.1 condensed

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?x = random_element(Z3,5)? \\
 & \verb?x? \\
\cZpCR
 & \verb?...11111? \\
%\cZpFP
% & \verb?...00000000000000011111? \\
\cZpLC
 & \verb?...11111? \\
\end{tabular}}

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?3*x? \\
\cZpCR
 & \verb?...111110? \\
%\cZpFP
% & \verb?...000000000000000111110? \\
\cZpLC
 & \verb?...111110? \\
\cIn
 & \verb?x + x + x? \\
\cZpCR
 & \verb?...11110? \\
%\cZpFP
% & \verb?...000000000000000111110? \\
\cZpLC
 & \verb?...111110? \\
\end{tabular}}

@@

Something is lost however in \ZpCR when performing $x+2x$.

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?y = 2*x; y? \\
\cZpCR
 & \verb?...22222? \\
%\cZpFP
% & \verb?...00000000000000022222? \\
\cZpLC
 & \verb?...22222? \\
\cIn
 & \verb?x + y? \\
\cZpCR
 & \verb?...11110? \\
%\cZpFP
% & \verb?...000000000000000111110? \\
\cZpLC
 & \verb?...111110? \\
\end{tabular}}

The same phenomenon occurs when comparing the computation
of $x^3$ and $x \times x^2$.

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?x^3? \\
\cZpCR
 & \verb?...010101? \\
%\cZpFP
% & \verb?...00000010100000010101? \\
\cZpLC
 & \verb?...010101? \\
\cIn
 & \verb?y = x^2? \\
 & \verb?x * y? \\
\cZpCR
 & \verb?...10101? \\
%\cZpFP
% & \verb?...00000010100000010101? \\
\cZpLC
 & \verb?...010101? \\
\end{tabular}}

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?x = random_element(Z2,10)? \\
 & \verb?y = random_element(Z2,5)? \\
\cIn
 & \verb?u = x+y? \\
 & \verb?u? \\
\cZpCR
 & \verb?...10111? \\
%\cZpFP
% & \verb?...000000000000000000000011010111? \\
\cZpLC
 & \verb?...10111? \\
\cIn
 & \verb?v = x-y? \\
 & \verb?v? \\
\cZpCR
 & \verb?...01111? \\
%\cZpFP
% & \verb?...000000000000000000000011001111? \\
\cZpLC
 & \verb?...01111? \\
\end{tabular}}

@@

Now, let us compute $u+v$ (and observe that it is actually equal to $2x$).

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?u+v? \\
\cZpCR
 & \verb?...00110? \\
%\cZpFP
% & \verb?...0000000000000000000000110100110? \\
\cZpLC
 & \verb?...00110100110? \\
\cIn
 & \verb?2*x? \\
\cZpCR
 & \verb?...00110100110? \\
%\cZpFP
% & \verb?...0000000000000000000000110100110? \\
\cZpLC
 & \verb?...00110100110? \\
\end{tabular}}

@@

No loss in precision appears in \ZpLC, contrary to \ZpCR.
%We remark that \ZpFP also provides all the correct digits.

>>>>

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?x = random_element(Z3,5); x? \\
\cZpCR
 & \verb?...11111? \\
%\cZpFP
% & \verb?...00000000000000011111? \\
\cZpLC
 & \verb?...11111? \\
\end{tabular}}

@@

{\noindent \small
\begin{tabular}{rl@{\hspace{1.5cm}}rl}
\cIn
 & \verb?3*x? &
\cIn
 & \verb?x + x + x? \\
\cZpCR
 & \verb?...111110? &
\cZpCR
 & \verb? ...11110? \\
%\cZpFP
% & \verb?...000000000000000111110? \\
%\cZpFP
% & \verb?...000000000000000111110? \\
\cZpLC
 & \verb?...111110? &
\cZpLC
 & \verb?...111110? \\
\end{tabular}}

@@

%Something is lost however in \ZpCR when performing $x+2x$.
%
%\smallskip
%
%{\noindent \small
%\begin{tabular}{rl}
%\cIn
% & \verb?y = 2*x; y? \\
%\cZpCR
% & \verb?...22222? \\
%%\cZpFP
%% & \verb?...00000000000000022222? \\
%\cZpLC
% & \verb?...22222? \\
%\cIn
% & \verb?x + y? \\
%\cZpCR
% & \verb?...11110? \\
%%\cZpFP
%% & \verb?...000000000000000111110? \\
%\cZpLC
% & \verb?...111110? \\
%\end{tabular}}
%
%\smallskip

\noindent
\todo{Add a short explanation?}

The same phenomenon occurs for multiplication.
%when comparing the computation of $x^3$ and $x \times x^2$.

@@

{\noindent \small
\begin{tabular}{rl@{\hspace{1.5cm}}rl}
\cIn
 & \verb?x^3? &
\cIn
 & \verb?x * x * x? \\
\cZpCR
 & \verb?...010101? &
\cZpCR
 & \verb? ...10101? \\
%\cZpFP
% & \verb?...00000010100000010101? \\
%\cZpFP
% & \verb?...00000010100000010101? \\
\cZpLC
 & \verb?...010101? &
\cZpLC
 & \verb?...010101? \\
\end{tabular}}

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?x = random_element(Z2,10)? \\
 & \verb?y = random_element(Z2,5)? \\
\cIn
 & \verb?u, v = x+y, x-y? \\
 & \verb?u, v? \\
\cZpCR
 & \verb?(...10111, ...01111)? \\
\cZpLC
 & \verb?(...10111, ...01111)? \\
\end{tabular}}

@@

\noindent
Now, let us compute $u+v$ and compare it with $2x$.

@@

{\noindent \small
\begin{tabular}{rl@{\hphantom{\hspace{0.8cm}}}rl}
\cIn
 & \verb?u + v? &
\cIn
 & \verb?2*x? \\
\cZpCR
 & \verb?...00110? &
\cZpCR
 & \verb?...00110100110? \\
\cZpLC
 & \verb?...00110100110? &
\cZpLC
 & \verb?...00110100110? \\
\end{tabular}}

@@

\noindent
No loss in precision appears in \ZpLC, contrary to \ZpCR.
%We remark that \ZpFP also provides all the correct digits.
